Twisted graviton spectra of $AdS_4\times S^7$ and $AdS_7\times S^4$

### 2023-05-22 graviton spectra/content/br.tex
almost done with index

\begin{lem}\label{lem:m2flux}
Let
\[
 F_{M2} = \frac{6}{(2\pi i)^4} \frac{\sum_{a=1}^4 \bar{w}_a \d \bar{w}_1 \cdots \widehat{\d \bar{w}_a} \cdots \d \bar{w}_4}{\|w\|^{8}} \partial_z .
\]
Then the background where $\mu = N F_{M2}$ and $\gamma = 0$
satisfies the above equations of motion in the presence of a stack of $N$ M2 branes:
\begin{align*}
\dbar (N F_{M2}) + \frac12 [N F_{M2}, N F_{M2}] & = N \Omega^{-1} \delta_{w=0} \\
\div (N F_{M2}) & = 0  .
\end{align*}
Here we set all components of the field $\gamma$ equal to zero (as well as the fields $\nu,\beta$). 
\end{lem}

@@

\begin{lem}
\label{lem:ads7flux}
Let
\[
F_{M5} = \frac{1}{(2\pi i)^3} \frac{\bar{w}_1 \d \bar{w}_2 \wedge \d t - \bar{w}_2 \d \bar{w}_1 \wedge \d t + t \d \bar{w}_1 \wedge \d \bar{w}_2}{(\|w\|^2 + t^2)^{5/2}} \wedge \d w_1 \wedge \d w_2
\]
Then, $\del\gamma = N F_{M5}$, $\mu = 0$, and $\nu = 0$ satisfies the equations of motion in the presence of a stack of $N$ M5 branes sourced by the term $N \delta_{w_1=w_2=t=0}$:
\begin{align*}
\dbar (NF_{M5}) + \d_{\R} (NF_{M5}) & = N \delta_{w_1=w_2=t=0}  \\ 
(NF_{M5}) \wedge (NF_{M5}) & = 0 .
\end{align*}
Here, we set all components of the field $\mu$ equal to zero (as well as the fields $\nu,\beta$). 
\end{lem}

@@

Part of our goal in the remainder of the paper is to justify conjectures \ref{conj:ads4} and \ref{conj:ads7}.
\end{document}

>>>>

\begin{lem}\label{lem:m2flux}
Let
\beqn\label{eqn:FM2}
 F_{M2} = \frac{6}{(2\pi i)^4} \frac{\sum_{a=1}^4 \bar{w}_a \d \bar{w}_1 \cdots \widehat{\d \bar{w}_a} \cdots \d \bar{w}_4}{\|w\|^{8}} \partial_z .
\eeqn
Then the background where $\mu = N F_{M2}$ and $\gamma = 0$
satisfies the above equations of motion in the presence of a stack of $N$ M2 branes:
\begin{align*}
\dbar (N F_{M2}) + \frac12 [N F_{M2}, N F_{M2}] & = N \Omega^{-1} \delta_{w=0} \\
\div (N F_{M2}) & = 0  .
\end{align*}
Here we set all components of the field $\gamma$ equal to zero (as well as the fields $\nu,\beta$). 
\end{lem}

@@

\begin{lem}
\label{lem:ads7flux}
Let
\beqn\label{eqn:FM2}
F_{M5} = \frac{1}{(2\pi i)^3} \frac{\bar{w}_1 \d \bar{w}_2 \wedge \d t - \bar{w}_2 \d \bar{w}_1 \wedge \d t + t \d \bar{w}_1 \wedge \d \bar{w}_2}{(\|w\|^2 + t^2)^{5/2}} \wedge \d w_1 \wedge \d w_2
\eeqn
Then, $\del\gamma = N F_{M5}$, $\mu = 0$, and $\nu = 0$ satisfies the equations of motion in the presence of a stack of $N$ M5 branes sourced by the term $N \delta_{w_1=w_2=t=0}$:
\begin{align*}
\dbar (NF_{M5}) + \d_{\R} (NF_{M5}) & = N \delta_{w_1=w_2=t=0}  \\ 
(NF_{M5}) \wedge (NF_{M5}) & = 0 .
\end{align*}
Here, we set all components of the field $\mu$ equal to zero (as well as the fields $\nu,\beta$). 
\end{lem}

@@

%Part of our goal in the remainder of the paper is to justify conjectures \ref{conj:ads4} and \ref{conj:ads7}.
\end{document}
